---
title: "Indonesia Jarvis Bango"
author: '[Gourab](https://twitter.com/gc_dataStart)'
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    theme: cerulean
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,results = T)
req_packages <- c("readxl","magrittr","tidyverse","dplyr","ggplot2","knitr","kableExtra","webshot","hablar","ggplot2")
sapply(req_packages,library,character.only=T)
```

# Introduction

__Indonesia Jarvis Bango__ report provide the users an overview about the data blending process which has been built using the __R Software__ and the packages . The report has been built using the __`r R.version.string`__.

The data blending model is built for the Indonesia `Savoury` brand __`Bango`__ which falls under `Seasoning` sector.

__`NOTE:The R project has been developed for the data blending of the Internal source Key Performance Indicators (KPI's)`__

## Data Sources (Summary Snapshot)

```{r DS,echo=F}
  current_working_directory <- getwd()
  file_name <- "KPI List Jarvis ID.xlsx"
  kpi_data <- readxl::read_xlsx(paste0(current_working_directory,"/",file_name))
  ds_list <- unique(kpi_data$Source_Type)
  ds_internal <- unique(kpi_data[kpi_data$Source_Type==ds_list[1],2])
  ds_external <- unique(kpi_data[kpi_data$Source_Type==ds_list[2],2])
  kpi_internal <- unique(kpi_data[kpi_data$Source_Type==ds_list[1],3])%>%dplyr::rename(`Internal_KPI's`=KPI_List)
  kpi_external <- unique(kpi_data[kpi_data$Source_Type==ds_list[2],3])%>%dplyr::rename(`External_KPI's`=KPI_List)
  count_internal <- count(kpi_internal)
  count_external <- count(kpi_external)
  
```
The Input data sources which the data blending process requires has been classfied broadly into two sources __`r ds_list[1]`__ and __`r ds_list[2]`__ data sources.The **Internal** data sources primarily is __`SAP BW`__ with **External** covering sources such as __`Nielsen ,Kantar,Milward Brown(BGS),Media`__.

The list of **Internal** data sources are mentioned as below 
```{r}
head(ds_internal,n=nrow(ds_internal))
```
The list of **External** data sources are mentioined as below 
```{r} 
head(ds_external,n=nrow(ds_external))
```

For our understanding lets take a look into  **Internal** and **External** Key Perfomance Indicators (KPI's) 

**First 10 Internal and External KPI's**
```{r first KPI}
head(kpi_internal,n = 10)
head(kpi_external,n=10)
```

**Last 10 Internal and External KPI's**

``` {r last KPI}
tail(kpi_internal,n = 10)
tail(kpi_external,n=10)
```
The __`ID Jarvis bango`__ model in total has __`r sum(count_internal,count_external)`__ KPI's with **Internal** and **External** sources having __`r count_internal`__ and __`r count_external`__ number of KPI's respectively.

## Project Parameters

The __`ID Jarvis Bango`__ project currently has 63 models which has been created based on various parameters as defined by the business.The models are based on the following paramters.

1.Channel __`Modern Trade (MT),General Trade (GT) Total indonesia`__.

2.Region __`Central & East Java (cej), Other Islands (oi), Sumatera (sumatera), West Java (wj)`__.

3.Sub Channel __`Mini Market, Hyper and Super Market (HSM)`__ .

4.Account __`Alfamart,Careffour,Indomart`__.

5.Packgroup 
```
Bango Manis Big pouch(bmbp), Bango Manis Medium Pouch (bmmp), Bango Manis Big Sachet (bmbs)
Bango Manis Small pouch (bmsp),Bango Manis Medium Bottle (bmmb) ,Bango Manis Small Bottle (bmsb)
```
6.Basepack
```
BANGO KECAP MANIS PEDAS 135ML(bkmp135),BANGO KECAP MANIS PEDAS 220ML(bkmp220)
BANGO SOY/OYSTER/FISH SAUCE MANIS 60ML(bsofs60),BANGO KECAP MANIS 135ML(bkm135)
BANGO SOY/OYSTR/FISH SUCE MNIS SCHT 30ML(bsofms30),BANGO SOY/OYSTER/FISH KECAP MANIS 580ML(bsof580)
BANGO KECAP MANIS 275ML(bkm275),BANGO KECAP MANIS 620ML(bkm620),BANGO KECAP MANIS 220ML(bkm220)
```

## Internal Data Sources (Deep Dive)
*****


### Background

__INTERNAL DATA SOURCES__ are the legacy source systems present in Unilever data ecosystem providing key information on Sales, Financials & other business information. The Information is only available to Unilever and is Private & Confidential in nature. Access to these data sources are managed by Unilever IT teams based on appropriate approvals.

### Internal Data Sources  


#### Primary Sales (SAP BW)
The primary sales refers to the sales which has been done by Unilever directly to the distributors. The Primary sales data are fetched from __`SAP BW`__ system. 

##### Key Performance Indicator (KPI's) list
```
Base KPI's : Gross Sales Value(GSV),Net Invoice Value (NIV),Sales Quantity(PCS)
Derived KPI's : Sales Quantity(KG),Sales Quantity (Tonns)

```

 __`Sales Quantity(KG)`__ and __`Sales Quantity(Tonns)`__ KPI's are calculated as   

```
Sales Quantity(KG) = Sales Quantity*conversion_factor
Sales Quantity(Tonn) = Sales Quantity(KG)/1000

```
#### Secondary Sales (SAP BW)
The secondary sales refers to the sale which has been done by Unilever to the retailers. The Secondary sales data are fetched from __`SAP BW`__ system.

##### Key Performance Indicator (KPI's) list 

```
Base KPI's : Secondary Sales Value , Secondary sales Volume
Dervided KPI's : Secondary Sales Volume(KG),Secondary Sales Volume(Tonns)

```
__`Secondary Sales Volume (KG)`__ and __`Secondary Sales Volume(Tonns)`__ KPI's are calculated as

```
Secondary Sales Volume(KG) = Secondary Sales Volume*conversion_factor
Secondary Sales Volume(Tonns) = Secondary Sales Volume(KG)/1000

```

#### Secondary Stocks (SAP BW)
<intro> The Secondary Stock

##### Key Performance Indicator (KPI's) list

```
Base KPI's : Secondary Stock Volume , Secondary Stock Value [@ DT Rate.] 
Derived KPI's : Secondary Stock Volume(KG) ,Secondary Stock Volume(Tonns)

```
__`Secondary Stock Volume (KG)`__ and __`Secondary Stock Volume(Tonns)`__ KPI's are calculated as

```
Secondary Stock Volume(KG) = Secondary Stock Volume*conversion_factor
Secondary Stock Volume(Tonns) = Secondary Stock Volume(KG)/1000

```

#### Dispatch Rate (SAP BW)
<intro> The dispatch rate 

##### Key Performance Indicator (KPI's) list

```
Base KPI's : Original Qty , Final Customer Expected Qty , Dispatched Qty
Derived KPI's : Dispatch Rate (DR) , Dispatch Rate (DROO)

```
__`Dispatch Rate (DR)`__ and __`DROO`__ are calculated as

```
Dispatch Rate (DR) = Dispatched Qty/Final Customer Expected Qty*100 
Dispatch Rate (DROO) = Dispatched Qty/Original Qty*100
```
#### Itrust 
<intro> 

##### Key Performance Indicator (KPI's) list

```
Base KPI's :
Derived KPI's : Itrust Line , Itrust Total , Itrust %

```
__`Itrust Line`__ is calculated as mentioned below 

```
For each observation in the dataframe
if::
 Final CRR = 0 then Itrust Line = 0
else::
 Stock CS > Final CRR then Itrust Line = 1 else 0

```
__`Itrust Total`__ is calculated as mentioned below

```
For each observation in the dataframe
if::
 Final CRR ==0 then Itrust Total = 0 else 1
```
__`Itrust %`__ is calculated as mentioned below
```
Itrust Line % = Itrust Line/ Itrust Total * 100
```


## Bango General Trade (GT) Model 
****

### Introduction

```{r GT,echo=FALSE}
bango_gt <- tibble::as_tibble(read_xlsx(paste0(getwd(),"/formated_total_bango_gt.xlsx")))
gt_kpi <- hablar::convert(bango_gt,num(`Bango GT_GSV`:ncol(bango_gt)))
gt_kpi <- dplyr::select(bango_gt,c(`Bango GT_GSV`:ncol(bango_gt)))
gt_data <- dplyr::select(bango_gt,c(Month,Channel,`Bango GT_GSV`:`Bango_I Trust %`))
```
The Bango GT model is the model which calculates the internal KPI's at __`Channel`__ level for the General Trade or Distributive trade . For the Bango GT model we have total __`r ncol(gt_kpi)`__ internal KPI's.

### Internal KPI's summary

The Internal KPI's list are as follows 
```{r gt_bango,echo=F}
kpi_names <- as.data.frame(colnames(gt_kpi[-1,1:ncol(gt_kpi)]))
```
```{r kpi_list,echo=F}
x <- "kPI_Name"
colnames(kpi_names) <- x
head(kpi_names,n=nrow(kpi_names))
```

__`The 5 numbers summary for each KPI's is mentioned as below`__
```{r}
summary(gt_kpi)
```
## Bango Mordern Trade (MT) Model 
****

### Introduction

```{r MT,echo=FALSE}
bango_mt <- tibble::as_tibble(read_xlsx(paste0(getwd(),"/formated_total_bango_mt.xlsx")))
mt_kpi <- dplyr::select(bango_mt,c(`Bango_GSV`:ncol(bango_mt)))
bango_mt <- hablar::convert(bango_mt,num(`Bango_GSV`:ncol(bango_mt)))

mt_data <- dplyr::select(bango_mt,c(Month,Channel,`Bango_GSV`:ncol(bango_mt)))
```
The Bango MT model is the model which calculates the internal KPI's at __`Channel`__ level for the Mordern Trade. For the Bango MT model we have total __`r ncol(mt_kpi)`__ internal KPI's.

### Internal KPI's summary

The Internal KPI's list are as follows 
```{r mt_bango,echo=F}
kpi_names <- as.data.frame(colnames(mt_kpi[-1,1:ncol(mt_kpi)]))
```
```{r kpi_list,echo=F}
x <- "kPI_Name"
colnames(kpi_names) <- x
head(kpi_names,n=nrow(kpi_names))
```

__`The 5 numbers summary for each KPI's is mentioned as below`__
```{r}
summary(mt_kpi)
```
