---
title: "Indonesia Jarvis Bango"
author: '[Gourab](https://twitter.com/gc_dataStart)'
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,results = T)
req_packages <- c("readxl","magrittr","tidyverse","dplyr","ggplot2","knitr","kableExtra")
sapply(req_packages,library,character.only=T)
```

## Introduction

__Indonesia Jarvis Bango__ report provide the users an overview about the data blending process which has been built using the __R Software__ and the packages . The report has been built using the `r R.version.string`.

The data blending model is built for the Indonesia `Seasoning` sector `Savoury` brand `Bango`.

`NOTE:The R project has been developed for the data blending of the Internal source Key Performance Indicators (KPI's).`

## Data Sources

```{r DS,echo=F}
  current_working_directory <- getwd()
  file_name <- "KPI List Jarvis ID.xlsx"
  kpi_data <- readxl::read_xlsx(paste0(current_working_directory,"/",file_name))
  ds_list <- unique(kpi_data$Source_Type)
  ds_internal <- unique(kpi_data[kpi_data$Source_Type==ds_list[1],2])
  ds_external <- unique(kpi_data[kpi_data$Source_Type==ds_list[2],2])
  kpi_internal <- unique(kpi_data[kpi_data$Source_Type==ds_list[1],3])%>%dplyr::rename(`Internal_KPI's`=KPI_List)
  kpi_external <- unique(kpi_data[kpi_data$Source_Type==ds_list[2],3])%>%dplyr::rename(`External_KPI's`=KPI_List)
  count_internal <- count(kpi_internal)
  count_external <- count(kpi_external)
  
```
The Input data sources which the data blending process requires has been classfied broadly into two sources `r ds_list[1]` and `r ds_list[2]` data sources.The **Internal** data sources primarily is `SAP BW` with **External** covering sources such as `Nielsen ,Kantar,Milward Brown(BGS),Media`.

The list of **Internal** data sources are mentioned as below `r kable(ds_internal)%>%kable_styling()`. The list of **External** data sources are mentioined as below 
`r kable(ds_external)%>%kable_styling()`.

For our understanding lets take a look into  **Internal** and **External** Key Perfomance Indicators (KPI's) 

**First 10 Internal and External KPI's**
```{r first KPI}
head(kpi_internal,n = 10)
head(kpi_external,n=10)
```

**Last 10 Internal and External KPI's**

``` {r last KPI}
tail(kpi_internal,n = 10)
tail(kpi_external,n=10)
```
The `ID Jarvis bango` model in total has `r sum(count_internal,count_external)` KPI's with **Internal** and **External** sources having `r count_internal` and `r count_external` number of KPI's respectively.

## Let's Deep Dive

The `ID Jarvis Bango` project currently has 63 models which has been created based on various parameters as defined by the business.The models are based on the following paramters.

1.Channel `Modern Trade (MT),General Trade (GT) Total indonesia`.

2.Region `Central & East Java (cej), Other Islands (oi), Sumatera (sumatera), West Java (wj)`.

3.Sub Channel `Mini Market, Hyper and Super Market (HSM)` .

4.Account `Alfamart,Careffour,Indomart`.

5.Packgroup 
```
Bango Manis Big pouch(bmbp), Bango Manis Medium Pouch (bmmp), Bango Manis Big Sachet (bmbs)
Bango Manis Small pouch (bmsp),Bango Manis Medium Bottle (bmmb) ,Bango Manis Small Bottle (bmsb).
```
6.Basepack
```







```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
